\chapter{Chronicler's Log}

\paragraph{14. October, 7:15; Train to Lenzburg}
It was a dark and story night,\ldots well it \emph{was} dark.
The storm was busy elsewhere, or \emph{is}, if you prefer present tense.
Once again, the nagging feeling of having forgotten something important and having left that thing somewhere near the coffer, but not quite inside it, looms over the back of my head.
I silence it with wisdom.
As long as civilization holds, you need but a passport, a credit card and some language skills to survive.
Well, maybe a clean set of clothes helps.
Do not try to go into a store naked.
Though\ldots if they are real businesspeople they would just show you to the clothes department.

\paragraph{14. October, 11:30; Plane to Singapore}
We met up, checked in.
Security checks, passport control and passport control.
Still some of the daily life we are leaving stowed behind us clings to the conversations.

Now we are stuffed into the double layered plane.
Bottom layer.
Together with other sardines.
A ball of rice was consumed, tasted delicious but fleeting.
We now wait for departure, arrival, maybe the onset of oblivion.

There is not enough space to put all the cushion and covers you get handed in this thing.

Correction: If you store them under your seat, there is.

\paragraph{15. October, Darkness; Plane to Singapore}
We are somewhere above India, nearing the coast.
Though my travel screen is frozen over Georgia.
I am writing in the dark, the reading light is too bright to be sensitive; using the LCD screen backlight to write.
Or rather - a pen lit by said backlight.
Have not been able to sleep.
Have not found any good codenames for the crew either.
At least the toilet paper is safely stowed away.

Flying always seems surreal.
You can travel halfway around the globe.
In a day's time.
In 80 days around the world.
If I did remember the name of the guy who wrote it, I would be guessing him to be somewhat perplexed if he had known.
People always wanted to see the end of the world.
Turns out, the end of the world is right where you started.
Taunting you: "Wanna go again?"
Maybe it had been better if the world actually turned out to be a disc.

\paragraph{15. October, 5:10; Still on the plane}
Had breakfast, nothing to report.
Red October broke his entertainment system, something to report.

\begin{center}
\begin{tabular}{||c||}
\emph{Achievement unlocked}\\
"Tech Support!"\\
\multicolumn{1}{||p{0.8\textwidth}||}{\footnotesize - Brick the entertainment system on an A380} \\
\end{tabular}
\end{center}

\paragraph{15. October, 17:30; Plane to Sydney}
After a sheer neverending cycle of breakfast-lunch eatery, we are finally nearly there.
Weather outside seems horribly bright.
Red October is getting sunburn just thinking about leaving the plane.
Well, the sky is blue and motivation is high.

\paragraph{15. October, 19:45; Car rental lot}
Aqcuired a van, spacey.
Met up with The Preceptress, the game is on.

We just got overtaken by a car sporting WOM 837 on the plate, emph{coincidence}?.

GPS navigation powered up, now navigating Sydney.

We now have a way description and a navigational system, cleary violating navigation 101: Never bring 2 compasses, either bring one or bring three.
If two compasses disagree, you never know which one to trust.

\paragraph{16. October, 0:10; Travelodge room 502}
First night in town, ate world's second greatest Burgers at \emph{grill'd Healthy Burgers}.
Finished up with cider and Cuba Libre, though our womenfolk only had a Margherita.

Though it was just a short night out, we already saw a smorgasboard of diversity:
Drag queens, gay people, women dressed in short skirts, all kinds of ethnicities.
Seems impossible to distinguish the natives from the tourists.

Though you can get liquor in most restaurants, some proudly proclaim BYO on liquor bottles, or wine for that matter.
This in its turn prompting businessmen to open bottle shops, where you can buy bottles, which are then brought to where you eat.

\paragraph{16. October, 12:10; The Rocks - Wharf 3}
Not that bright an idea, going sightseeing on a sunday.
The is booked tightly.
And we lost sight of The Bomber and The Gadgeteer during boarding.

\paragraph{16. October, 12:35; Ferry to Manly}
We're off on the waves.
Lining the coast.
Apartments and villas sprinkle the seaside hills.
Beaches and seas of boat masts hint at expensive living between the forested cliffs.

There is a nice view of the Opera House and that huge bridge of which nobody bothered to tell me the name.
Well, to be fair, I did not ask.

Now the coast line turns to cliffs, except those parts that look more like concealed fortification than natuarally occurring rock formations.

And there is sailing and buoys, maybe some are training for the next big regatta and others are just waiting for an opportunity to feed their rich husband to the sharks.

And then there is a speedboat, dashing from one ship's trail to another soaking its passengers in the ensuing spray as it goes.

I wonder whether estate prices for fish homes below have plummeted since they established the ferry lines.
After all, we are complaining about air plane noise in \emph{our} homes\ldots{}

\paragraph{16. October, 16:10; Manly Ferry to Sydney}
Spent an afternoon walking about Manly and eating spicy chicken.
Learned that swimming is discouraged for 24 hours after heavy rain due to pollution.
The nature of the pollution remained unknown.
The island's name is a near endless source of pun based humor and the local business and tourist organisations are tapping into it heavily.
I'm unsure whether by accident or deliberately.
Also, surfing seems to consist og 50\% waiting, 25\% standing on wood and 25\% falling into water.

\paragraph{16. October, 18:34; Travelodge room 502}
Returned, bought supplies, passed ny night noodle market, now waiting for organisation.
Excursion at 19:00.

\paragraph{16. October, 23:00; Travelodge room 502}
Waited to finish booking hotels, we seem to be traveling in-season, hotels are slightly overbooked.
Went for Thai food, delicious.
Red October got recognized by the owner, showed him an obviously Italian teddy bear.
Was able to save us by telling them we were Swiss.
He did not ask for a clock or chocolate.
Maybe he did not believe me.

Red October and The Bomber went drinking afterwards.
Now they are sitting in our room, cider in hand.
They forgot it is forbidden to drink in public\ldots{}

\paragraph{17. October, 11:15; On the road to Wagga Wagga}
After Sydney was done confusing the heck out of our navigation system, we are now trucking the countryside after leaving the suburbs.

Roadkill counters are steadily increasing.
Had 4 kangaroos and a wombat so far.

\begin{center}
\begin{tabular}{||c||}
\emph{Achievement unlocked}\\
"Wild Unlife"\\
\multicolumn{1}{||p{0.8\textwidth}||}{\footnotesize - Have the first native animal you see be roadkill} \\
\end{tabular}
\end{center}

\paragraph{17. October, 11:30; Road through Jenolan Forest}
We are more or less the only car on the immediate road.

We are passing rolling hills, eucalyptus trees, pine trees, eucalyptus trees and pine trees.

\paragraph{17. October, 13:20; Jenolan Caves}
Gone spelunking, or near-spelunking.
There was a large cave, a dam with emerald waters - or maybe turquoise waters, who can tell these days.
There were eucalyptus trees in a large clearing further down the valley.
The Gadgeteer scared a dragon, then photographed it.
The rest just scared regular lizards.

Pecularity: Part of the walkway through the cave daoubled as road.
A sign advised us to use extreme care when passing.
Had only regular care at our disposal, survived nonetheless.

When we got back to the car, one of the guided tours was just starting.
They were calling for "chicken holders" - comedy ensued.

\texttt{>>> FILE ACCESS ERROR - MISSING IMAGE <<<}

\paragraph{17. October, 14:30; Oberon}
Picked up a sammitch, a pastie, two pies, two hamburgers and a chicken salad.

The pies will most likely end up in trash, leaving The Preceptress hungry and the chicken salad was a bit improvised.
Rest was good though.

Fascinatingly, parking forwards is prohibited.

\paragraph{17. October, 21:40; Motor Inn Wagga Wagga}
We arrived at sunset.
Tires digging through the gravel in the driveway.
Doors looked barred.
A few cars rust silently in the parking lot.
Our headlights fall dark.
Car doors slam shut.
Nobody notices our arrival but the cold evening breeze.
The outer door creaks as we enter.
The inner door slams shut.
A dark saloon looms beyond.
Chairs stored on the tables.
It was swept, dust had not yet settled in.
We walked past a flickering TV screen, sume kids rustled around.
Beyond, the reception desk.
We checked in.

Dinner at pub.
The Bomber fails to buy Skittles from a dispenser.
Outside LEDs hanging from a tree glitter in the night.

\texttt{>>> DISTANCE TRAVELED BY CAR: 600km - totals 600km <<<}

\paragraph{18. October, 9:40; Highway to Cooma}
This is cow country, the secret cow level, cowtopia, the great grazing grounds,
the place a good cow is reincarnated to when it has been made into enough delicious burgers.
In Switzerland we have a label "Freilandhaltung", when they are kept outside, on the field.
Compared to the rolling grasslands we pass now, where the cattlegrounds go on until they meet the horizon,
the label seems like a bad joke.

If you ever plan on reincarnating as a cow. Try to get a spot in Australia.
You are going to get eaten anyways.
Might as well choose a nice place to stay until that time.

\paragraph{18. October, 11:35; Black Perry Lookout}
We now have even seen \emph{live} cangaroos and emus and have made our way over the Snowy Mountain Road.

A quick stop at the lookout shows a lot of foresty mountainside.

\texttt{>>> FILE ACCESS ERROR - MISSING IMAGE <<<}

And we greeted old people which seem to follow plans analogous to ours.

Since we are going to drive onward now, I continue writing in the back seat while insane bikers pass by.
Should work, bit I notice my handwriting suffers during the bumpy ride.

One stop back we strolled down the side of a lake.
Fairytale weather and a tree which could have sprung from any jolly children's story later we were back on the road.

\texttt{>>> FILE ACCESS ERROR - MISSING IMAGE <<<}
 
\paragraph{18. October, 13:40; Snake Trail}
We hit a snake trail, diverting from the highway to the left.
Gravel road is bumpy.

The pen rolled under the seats somewhere.
I am unable to find it, so I am using a pencil for this entry.

We ditched the plan to take the scenic drive along the mountainside.
Would have taken us the whole day just for the drive and no time for exploring.

So we went spelunking.
Big wet cold cave.
Contained a wig.
Entrance hall collapsed some time ago.
Owner did not come around to renovate.
Must have come on hard times - the lighting was sparse and most of the rooms were damp.
At least they had outdoor heated pool, but be skipped that.
Always prioritize food.
Just noticing.
If I keep this speed of logging up, I might fill the log book before wee are back out.

Maybe I should remember to hit an office supply shop for a spare paper blank.

The toilet paper is still untouched.

\paragraph{18. October, 15:00; Exiting Cabramurra}
At Australia's highest up village thae café closes it's kitchen at 1400.
We settled for Cup Noodles - well - some of us did.
The others maintian their sugar levels with sweets and candy bars.

We skipped photographing the town sign and I found my pen.

\texttt{>>> DISTANCE TRAVELED BY CAR: 275km - totals 875km <<<}

\paragraph{19. October, 9:00; Exiting Cooma}
Had delicious (and plentiful) dinner last night, followed by an attempt at wireless internet.

\begin{center}
\begin{tabular}{||c||}
\emph{Achievement unlocked}\\
"Evolution 101"\\
\multicolumn{1}{||p{0.8\textwidth}||}{\footnotesize - Run over a Cuckaborra} \\
\end{tabular}
\end{center}

\begin{center}
\begin{tabular}{||c||}
\emph{Achievement unlocked}\\
"Backseat Driving"\\
\multicolumn{1}{||p{0.8\textwidth}||}{\footnotesize - Start a Flame War with the driver} \\
\end{tabular}
\end{center}

Wireless internet was slooow.
Too slow for Lotus Notes, preventing The Bomber to check his work mail.
Too slow for GMX, preventing Lady Roadkill to check her private mail.
Almost too slow for GMail enabling me to do reauthentification at snail's speed.

While I was logging we had our first road kill.
It might have been a good thing.
That Cuckaborra was too stupid for life.
Just waiting in the middle of the road, staring at the set of wheels approaching at high speeds.
Maybe it was suicidal.
Who knows.

\paragraph{19. October, 9:25; On the road}
I think we just passed a road called \emph{No Through Road}.

And we missed the exit to Springfield.

\paragraph{19. October, 12:22; Still on the road}
Driving, driving, driving - on roadkillless raods.
Passing meadows, fences, forests, sheep, cows, cars, horses, birds, traffic signs and concealed entrances.

Trying to point out to the others what I have dubbed \emph{Sheep Launch Pads}: Small ramps that are directed outwards from a corral and lead to virtually nowwhere.
Suppose they are intended to serve as a way to get sheep out to the meadow without giving them any way to come back.

\paragraph{19. October, 15:40; Mallacoota}
Starting to get the hang of Australian serving sizes.
Ordering a single meal or a large side usually is enough.

Took a stroll on the beach.
The Bomber and me were thwarted from crossing to the other shore by Six Meters Of Water.
Noticeable amounts of shell were discovered.
There was beautiful sea, sand and waves.
Work stress debuff starting to wear off.
The Cameraman took about 2 Minutes of me talking Irish on the shore.

No, I am not going to transcribe.

\paragraph{19. October, 17:15; Road to Lake's Entrance}
The sun is descending slowly on a sky barren of clouds.
As we pass the flickering shadows of the forest we plow through legions of insects swarming in the dry spring air.

\texttt{>>> FILE ACCESS ERROR - MISSING IMAGE <<<}

\begin{center}
\begin{tabular}{||c||}
\emph{Achievement unlocked}\\
"Buzzkill"\\
\multicolumn{1}{||p{0.8\textwidth}||}{\footnotesize - Squish 100 bugs with your wind shield} \\
\end{tabular}
\end{center}

\begin{center}
\begin{tabular}{||c||}
\emph{Achievement unlocked}\\
"Beyond Inadequate Bovine Rivers"\\
\multicolumn{1}{||p{0.8\textwidth}||}{\footnotesize - Pass Bad Cow Creek} \\
\end{tabular}
\end{center}

\paragraph{19. October, 17:30; Fluffy Forest} 
Passing through a forest which seems to have burnt down.
However from the dead trunks the leaves just sprout once again.
The whole forest looks like green corran candy sticks.

\emph{It's so fluffy!}

\texttt{>>> FILE ACCESS ERROR - MISSING IMAGE <<<}

\begin{center}
\begin{tabular}{||c||}
\emph{Achievement unlocked}\\
"The Best Things In Life\ldots{}"\\
\multicolumn{1}{||p{0.8\textwidth}||}{\footnotesize - Obtain free good quality wireless Internet access} \\
\multicolumn{1}{||p{0.8\textwidth}||}{\footnotesize - You must have already had paid bad quality wireless Internet access before to unlock this achievement} \\
\end{tabular}
\end{center}

\paragraph{19. October, 22:25; Lake's Entrance, Room 5}
First life sunset in Australia.
We saw it from the beach.
Romantic.
We had the whole program.
Rolling waves.
Endless horizon.
The sun going through the orange tones down to red.
Boats glistening in the duskish shine.
Masts rocking in the evening tide.
The frequency of photographs taken peaked.
The remaining digital storage capacity tanked.

We went for Mexican this night.
Had to find out that any dish that costs about 15 Australian Dollars will be a regular sized meal.
Anything which costs more will be challenging to finish.
At least this is the case while away from the big cities.

\texttt{>>> DISTANCE TRAVELED BY CAR: 452km - totals 1325km <<<}

\paragraph{20. October, 9:30; Lake's Entrance, Gas Station}
The Bomber, Red October and me went for a run on the beach at dawn.
Damn I am out of shape.

Once again we refuel.
Must have burnt through a dozen dinosaurs already.
Damn van is a fuel guzzler.
And the fron grill is a war zone.
Or rather - a bug graveyard.
Now we are back on the raod.
Windshields wiped and tires pumped.

Melbourne awaits beyond the horizon.

\paragraph{20. October, 10:10; Road to Melbourne}
After six attempts which ended with the tablet pc crashing and losing the playlist, we finally found an app that does not crash, hang, stop playing when the display turns off or just drops the playlist randomly.
So we now have reliable music in the backgorund without having to rely on Aussie radio, which is - according to everyone in the car - just plain horrible.

\begin{center}
\begin{tabular}{||c||}
\emph{Achievement unlocked}\\
"\ldots{}whut?"\\
\multicolumn{1}{||p{0.8\textwidth}||}{\footnotesize - Misunderstand a road name and log Bad Cow Creek instead of Fat Cow Creek}\\
\end{tabular}
\end{center}

\paragraph{20. October, 10:35; Following the railroad tracks}
Australians must be really good at fencing.
Not the kind with sharp sticks.
The kind which involves putting up obstacles to keep wild or domestic life from crossing.

We are passing mile after mile of fences.
Either this keeps wildlife from wandering onto the road (with mediocre success) or it keeps cattle from walking more than a few miles in a sraight line.

The chines built the Great Wall, the Australians just built the Great Fence.

On another note, The Bomber found a better explanation for the \emph{Sheep Launch Pads}.
They are for loading and unloading lifestock into transporters\ldots{}
duh\ldots{}

\paragraph{20. October, 10:50; Sale}
Yes, we just passed Sale, the town.
Since the name was just too silly, we moved along.

\paragraph{20. October, 12:00; Road to Melbourne}
Somehow we ended up in Weird-Names-Country: Baw Baw Mountain, Drouin, Darnum, Robin Hood, Service Centre Bay - now wait, that is no town - Dadenoug, Labertouche.
Got\ldots{} to\ldots{} stop\ldots{} reading\ldots{} roadsigns.

\begin{center}
\begin{tabular}{||c||}
\emph{Achievement unlocked}\\
"Kevinism Country"\\
\multicolumn{1}{||p{0.8\textwidth}||}{\footnotesize - Pass "Sale"}\\
\multicolumn{1}{||p{0.8\textwidth}||}{\footnotesize - Pass "Fat Cow Creek"}\\
\multicolumn{1}{||p{0.8\textwidth}||}{\footnotesize - Pass "Robin Hood"}\\
\multicolumn{1}{||p{0.8\textwidth}||}{\footnotesize - Pass "Baw Baw Mountain"}\\
\multicolumn{1}{||p{0.8\textwidth}||}{\footnotesize - Pass "Wagga Wagga"}\\
\end{tabular}
\end{center}

\begin{center}
\begin{tabular}{||c||}
\emph{Achievement unlocked}\\
"40 Ton Tweezers"\\
\multicolumn{1}{||p{0.8\textwidth}||}{\footnotesize - witness two trucks overtake a third simultaneously on the left and right}\\
\end{tabular}
\end{center}

\paragraph{20. October, 13:00; Approaching Melbourne}
Traffic gets heavier as we cloase on target.
Wind keeps the driver on his toes, as does the lunatic driving style of the Aussie truckers.

We have been passing noise-sheltered suburbs for quite some time now.

\emph{Fucking big town, this Melbourne.}

\paragraph{20. October, 13:30; Hotel Alto Parking Lot}
Parking lot clocks in Melbourne run with pressure sensors.
At least that is what they are telling us.
We had no way of just waiting until Lady Roadkill and The Cameraman had checked in.
The authorities were right on our track, and after our moneys.

\texttt{>>> DISTANCE TRAVELED BY CAR: 317km - totals 1650km <<<}

\paragraph{20. October, 21:45; Melbourne, Room 404}

\begin{center}
\begin{tabular}{||c||}
\emph{Achievement unlocked}\\
"File Not Found"\\
\multicolumn{1}{||p{0.8\textwidth}||}{\footnotesize - Check in to room 404}\\
\end{tabular}
\end{center}

Arrived in hook-turn-notorious Melbourne city.
Hook turns are when you try to take a right turn from the lane on the extreme left.
And it looks like certain suicide when performed.

We split up for the city exploration sice Lady Roadkill had to organize her flight to New Zealand.
The rest went for a stroll and a coffee in Federation Square.
Though the buildings there were anything but square.
Supposedly the architect drove a few construction engineers to madness.

The city itslf reminds me of San Francisco or even Zurich, except this one feels more like a police state than both of the others.
In the evening we even saw a police car with a supposed sobering cell attached.
Scary prospects for drunkards.

went to a pub \emph{The Local Taphouse} to meet Lady Roadkill's aquaintances.
Had a nice evening with pub food in a pub that has a different selection of local beers every day.
The group tried a grand total of six beers and one cider.
The general 15 Dollar rule for meals held up, though in the city you have to up it by 3 Dollars.

The district the pub was in laeft an\ldots{} interesting impression. It looked a bit shabby, the buildings were mostly in a desolate state from the outside, yet nice from the inside.
The people seemed friendly if a bit loud for my tastes.

Bumped into a waiter at the end of the evening.
Even though I made him spill a drink, he kept being (overly) friendly.
Though he checked out my table afterwards, I guess he was checking if I might have had one or two drinks too many.

\paragraph{21. October, 14:15; Melbourne, Free Shuttle Bus}
The weather took a turn for the worse.
Lady Roadkill took up the opportunity to do some laundry, the rest decided to throw themselves at the rain.
Well, not really rain, it was more like overly enthusiastic fog.
We headed out for Chinatown, which was somewhat diasappionting, then went onward to Saint Patricks Cathedral.
Being archbishop of Melbourne seemd to be a dangerous job. Of the seven they have had so far, five already died and one seems to have quit the job before it could take the better of him.
Special thing about the cathedral: Wooden roof.

Now we sit reunited in the free tourist shuttle bud, which runs every 30 minutes, which translates to Australian as "every 25 minutes" which makes catching it quite of a waiting and gambling game.
We missed one because we decided to have a look at graffity lane.
There one of the fundamental truths about mankind was displayed.
Even when graffity is legal, artfully created pictures will still be skribbled over by idiots only capable of reliably misspelling their names.

Fun thing about technology and free bus rides: People will bring cameras and just film the road during the trip.
Maybe one should point out the existence of Google Street View.

\paragraph{21. October, 15:45; Melbourne, Free Tourist Shutte Stop 1}
Almost completed the circuit, since we did not get in at the official starting point to be gin with, we will stay on a few more stops.

Forgot to mention that we hit Melbourne Museum, got bummed out on the same old colonialism issues you have everywhere.
Saw some Melbournian history and a horse that seemed very Australian and very famous.
Though it died somehow in the USA.
Gotta look that up.
I guess it ended up covered in gravy and accompanied by chips courtesy of some angry mob bookies.

\paragraph{21. October, 23:05; Hotel Alto Room 404}
The horse died of an overdose of arsenic according to Wikipedia.
No evidence of a crime was ever found.

On another note we had (expensive) Japanese food for dinner.
The Australian serving sizes failed us this time.
Seems that Japanese food always comes in normal size servings, regardless of price.
Had Wagyu beef for dinner - delicious but pricey.

The we - minus Lady Roadkill - headed to the top of Eureka Tower.
The viewing facility was named Skydeck 88 and was reasonably high up.
Still too high up for me to feel comfortable on the terrace when the wind blew.
The view was nice though.
Lots of lighting and little cars moving in the streets and ways of slipping and crshing through a window and plummeting to \ldots{}
As I said before, waaay to high up to feel comfortable.

\begin{center}
\begin{tabular}{||c||}
\emph{Achievement unlocked}\\
"Point of No Return"\\
\multicolumn{1}{||p{0.8\textwidth}||}{\footnotesize - Witness someone propose a few hundred feet above solid ground}\\
\end{tabular}
\end{center}


\begin{center}
\begin{tabular}{||c||}
\emph{Achievement unlocked}\\
"Liberate Wall Street!"\\
\multicolumn{1}{||p{0.8\textwidth}||}{\footnotesize - Witness Wall Street protestors protesting}\\
\multicolumn{1}{||p{0.8\textwidth}||}{\footnotesize - Witness Wall Street protestors being cleared away by the police}\\
\end{tabular}
\end{center}




