\chapter{Extraction}

% 14th November until 20th November

\paragraph{14. November, past midnight; Shortly before landing in Singapore}
3 movies and a dinner later\ldots{}

Halfway\footnote{maybe a bit less} back to home.
We still have to survive changing planes.
Should go ok though.

Last time I checked on the toilet paper, it was holding together.

\paragraph{14. November, 3:10; Above Saudi Arabia}
Still 4 hours of flying to go.
We are racing dawn to Zurich, it is still pitch black outside and it is hard to think of something to write in the dead of night.

Pondering about daily life catching up to you.
Once again being able to use the cellphone to its fullest without ruining yourself.
Having a kitchen you actually cook in.
No cockroaches to greet you at your doorstep.

There are still about 20 pages left emtpy iin the log book.
But I do not have a gardener to pass it on to, so I guess they will stay empty.

Shutting down the light now, maybe I can get a few more hours of sleep.

\paragraph{15. November, 7:15; My Couch}
This is it, I am once again getting ready to work.
The souvenirs and leftover other stuff is piling on my kitchen table, the clothes are drying in the bathroom and I am wrapping up the logbook.

Not much more to write, just trying to postpone the realization that I will have to get up in a few minutes and catch my train.

This is The Chronicler.
Signing out.

\begin{center}
\begin{tabular}{||c||}
\emph{Achievement unlocked}\\
"Back Out"\\
\multicolumn{1}{||p{0.8\textwidth}||}{\footnotesize - Go to Australia and return"} \\
\end{tabular}
\end{center}
