\chapter{Week Four}

% 7th November til 13th November

\paragraph{7. November, 9:45; Highway to Gold Coast}
Writing after having had cider is lacking thoroughness.
Forgot to write about us sightseeing around Brisbane.
Lovely town, lots of flowers, fountains and parks, when you walk the right way.
They even have free outdoor swimming pools amidst ice creameries and flower laden walkways.
There are also quite a bunch of people around.
Could be because yesterday was Sunday.
Also, they got quite a few architecturally interesting bridges, some reserved to cyclists and pedestrians.
And of course, the design of some of those has supposedly driven a few engineers towards insanity.

\begin{center}
\begin{tabular}{||c||}
\emph{Achievement unlocked}\\
"Street of Negotiable Affection"\\
\multicolumn{1}{||p{0.8\textwidth}||}{\footnotesize - Drive past "Hooker Boulevard"} \\
\end{tabular}
\end{center}

\paragraph{7. November, 22:00; Yamba Waters Holiday Park}
Just noticed I accidentally stapled two pages together.
Maybe some future generation will interpret this as some occult writing ritual - until then I will just continue logging.

Today's menu was a light walk on the Gold Coast's beaches.
However the legions of skyscraper hotels built there did not cast their shadows anywhere useful, so The Gadgeteer ended up with another layer of sunburn.
Most prominent feature on the beach\footnote{besides the hotels lining it}, were the "no dogs allowed beyond this point" signs which were lined by dog tracks.

The second course was an expedition to a lighthouse, magnificent view of the cliff side and the sea spray.
Lots of stair climbing involved and the lighthouse was closed for tourists without a guide.
Well\ldots{} bought a "degradable" drink there.
I hope they were referring to the bottle and not its contents, the implications seem\ldots{} unpleasant.

Between courses there was driving - once again through sugar cane fields and past sugar cane mills.
We learned to recognize a nearby sugar mill by the omnipresent smell engulfing them, of which you get sick \emph{very} quickly.
It is described as a mixture of canned corn and wet pulped wood.

To top it off, we managed to do a late check-in here.
Had to retrieve our keys and such from a pin code locked safe at the reception.
Subways for dinner.
Toilet paper rill status unchanged.

Moral is a bit moody, the end of the trip is precasting its depressing shadow.
And the dark tendrils of work are already extending their merciless grasp towards The Bomber.

Thus is the circle of life.

\begin{center}
\begin{tabular}{||c||}
\emph{Achievement unlocked}\\
"Bloody Pulp"\\
\multicolumn{1}{||p{0.8\textwidth}||}{\footnotesize - Get sick of sugar cane plantations"} \\
\end{tabular}
\end{center}

\paragraph{8. November, 17:25; Styx River Forest Way}
It rains once again.
We just ducked unto the car as the shower hit us.
Dry in the car now.
Not a terribly spectacular day.
Walked around in another rain forest, walked above said rain forest and drove around the same rain forest.

We have been to lookouts, looked down on some more waterfalls and drove by even more waterfalls.

And then the rain forest thing again before the word preceding the forest came down on us.

At least\footnote{last?} we saw some wild kangaroos, some wild hares and - wait for it - a snake.
Just slithering there - all black and scaly.

On the track back a couple of cows blocked the road.
The Bomber hat to honk them off the road.

\begin{center}
\begin{tabular}{||c||}
\emph{Achievement unlocked}\\
"Three Cows Down"\\
\multicolumn{1}{||p{0.8\textwidth}||}{\footnotesize - Drive past three dead cows"} \\
\end{tabular}
\end{center}

\begin{center}
\begin{tabular}{||c||}
\emph{Achievement unlocked}\\
"Cowblocked"\\
\multicolumn{1}{||p{0.8\textwidth}||}{\footnotesize - Stop the vehicle because of cows blocking the road"} \\
\end{tabular}
\end{center}

PS: Do not enter the resting lodge on Lookout Point.
It is abuzz with flies.
They make for a somewhat unsettling atmosphere.

\paragraph{9. November, 23:55; Sydney, Travelodge}
We were driving again.
Most of the day, racing the sun to Sydney.
We were not doing anything else but driving.
Endless driving.
Even the roll of toilet paper got bored.

We only stopped a few times.
Loo breaks, refueling, more loo breaks.
At one stop I managed to soak myself by mishandling a public water spring.
I also bought tea there.
And Red October picked up an infantry magazine.
And there was a tank.
And then, more driving.

Before we ended up in Sydney City we drifted off to the Olympic Park.
It was big but lacked\ldots{} impressiveness.
Particularly the parks behind it.
We walked along a ring walkway above an abandoned quarry which was only not recycled as Olympic Park area because it had been colonized by rare frogs.
\emph{Very} rare frogs.

Then, at the hotel, the usual problem with double beds instead of twin beds and the bed sofa conundrum.
At least the Indian dinner we had was glorious.
And now they are looking for a restaurant that serves croc and kangaroo.

\begin{center}
\begin{tabular}{||c||}
\emph{Achievement unlocked}\\
"Writer's Block"\\
\multicolumn{1}{||p{0.8\textwidth}||}{\footnotesize - Fail to think of any interesting achievement all day"} \\
\end{tabular}
\end{center}

\paragraph{10. November, 16:55; Sydney, Travelodge Room 703}
Sydney!
First item of business: Rain.
So we moved the Blue Mountains to tomorrow.
Or rather we moved the excursion.
So today's menu: Shopping!

We hit the local mall.
Meh, they only had imported foods.
Bringing home Swiss chocolate from Australia: Fail.
The tourist traps slash souvenir shops were at least a \emph{little} more inventive.
Though they overshot a little when we browsed past the stuffed kangaroo balls\ldots{}
We secured some kangaroo jerky, some crocodile jerky and some macadamia nuts\footnote(unstuffed) besides other, stranger stuff\footnote{canned plushies}.

With bags full of nonsense we ventured on.
Found out that Chinese friendship costs about 6AU\$\footnote{at the Chinese Garden of Friendship} and then we visited the Aquarium where we saw Cuttlefish\footnote{Cuthulu-Face-Fish}, Dugongs\footnote{Sea Cows}, Sharks\footnote{Tooth-Face-Fish}, Crab\footnote{Not-Fish-With-Big-Claws-And-Huge-Spindly-Legs}, Small Penguins\footnote{Sub-Bird-Marine}, Sea Horses\footnote{Sea Horses} and water.

\paragraph{10. November, 16:55; Sydney, same room, same hotel}
Slightly tipsy.
Was unable to increase tipsiness due to Sydney closing its bottle shops at 9pm.
Horrible thing to do.
At least we got another dinner at grill'd out of it.
And we saw the Opera House.
Where the Organ needed 10 years to be built and 2 years to be tuned.
Possibly an indicator for Australian work morale.
Other than that, exploring the thing seems to the reserved for high society as most stairs are off limits for the public. 

\begin{center}
\begin{tabular}{||c||}
\emph{Achievement unlocked}\\
"The Circus is Back in Town"\\
\multicolumn{1}{||p{0.8\textwidth}||}{\footnotesize - Drive a KIA \emph{Grand Carnival} into Sydney"} \\
\end{tabular}
\end{center}

\paragraph{11. November, 23:45; Sydney, Travelodge, Room 703}
Today's menu was driving around the Blue Mountains, hopping from vista to vista and hiking a few meters below, above and around the mountain cliff side.
We have seen an Aborigine guy with a beard sitting around, playing didgeridoo and talking to the city people about the meaning of life.
Found the WLAN password of bakeries is \emph{sourdough} and once again, we have seen more bloody waterfalls.
They are everywhere.

Dinner!
We had teppanyaki with crocodile and kangaroo.
Crocodile tastes zesty and kangaroo reminds me of rabbit.

Highlight of the day was the heroic capture of a cockroach that wandered into out room.
We brought it down to the reception, basking in the whiteness of the receptionists face when presenting him the insect.
Compensation - besides an onslaught of insect spray - was not yet offered.
We are waiting on events to unfold.

\begin{center}
\begin{tabular}{||c||}
\emph{Achievement unlocked}\\
"The Unskittering"\\
\multicolumn{1}{||p{0.8\textwidth}||}{\footnotesize - Capture a cockroach"} \\
\end{tabular}
\end{center}

\paragraph{12. November, 10:50; Sydney, Travelodge, Room 703}
It is Christmas time\ldots{} without cold, snow or reindeers.
The shopping centers have already rolled out the nativity scenes and the Christmas cake.
And there are pianists playing in the big malls.

\begin{center}
\begin{tabular}{||c||}
\emph{Achievement unlocked}\\
"Don't Shoot The Pianist"\\
\multicolumn{1}{||p{0.8\textwidth}||}{\footnotesize - See a pianist play at a mall"} \\
\end{tabular}
\end{center}

\begin{center}
\begin{tabular}{||c||}
\emph{Achievement unlocked}\\
"Hits The Fan"\\
\multicolumn{1}{||p{0.8\textwidth}||}{\footnotesize - Run out of toilet paper in a hotel"} \\
\end{tabular}
\end{center}

\paragraph{12. November, 15:45; Sydney, Travelodge, Room 703}
Organized Vegemite, honey and bus tickets to Bondy Beach.
Also, as is tradition, we visited a war ship and a submarine.
Coincidentally both were anchoring next to the Sydney Maritime Museum.
So we looked at that as well.
Lots of ships and big corporations were already present in the old days.
These days we just have more gadgets and satellites up.
At least there were no waterfalls.
Just tales of ships and wrecks and voyages.

\paragraph{13. November, 0:30; Sydney, Travelodge, Room 703}
After an ungodly amount of pork ribs on Bondi Beach and witnessing the Australian police getting public drinkers to take their booze somewhere else, we were greeted another joyfully antenna wagging cockroach in our apartment.
It was promptly captured and redeemed for 2 free breakfast vouchers.
Final evening in Australia well spent.

\begin{center}
\begin{tabular}{||c||}
\emph{Achievement unlocked}\\
"From Cairns to Sydney"\\
\multicolumn{1}{||p{0.8\textwidth}||}{\footnotesize - Return your rental car after having driven it for 3736km"} \\
\end{tabular}
\end{center}

\paragraph{13. November, 15:45; Sydney, Airport, Gate 61}
We passed one of two security checks.
The Bomber is no linger with us, as we wait for boarding to start.
The dark claws of work claimed him and dragged him to Perth.
At least we got to play laser tag with him one last time before departure.
It was a sad thing to tell the dame at check-in time that he will not be coming.

We somewhat sucked at laser tag.
Sticking together and covering our backs might be secure, but it does not score as much points as blindly charging into battle and shooting whatever is moving.

We finished of the day's activities in the Royal Botanic Gardens and then inspected The Bomber's room at the Hilton.

Now we are giving our goodbye to Australia.
In a few minutes we will no longer be down under.

\begin{center}
\begin{tabular}{||c||}
\emph{Achievement unlocked}\\
"You Shoot Like My Grandmother"\\
\multicolumn{1}{||p{0.8\textwidth}||}{\footnotesize - Get beaten at laser tag by high schoolers"} \\
\end{tabular}
\end{center}
