\chapter{Week Three}

% 31th October til 6th November

\paragraph{31. October, about Midnight; Peppers Resort, Apartment 314}
The pen is down in the car, once again I am back up to using pencil.

It was a long day of driving, we destroyed roughly 600km of linear distance.
Highlights were an overly zealous construction project along the way.
We passed about half a dozen road works.
Also we crossed a dozen rail tracks which seemed to belong to the sugar cane cartel whose sugar cane plantations we were driving though.
Other than that there was a huge amount of coast and traffic and - well - a lot of driving involved.

At our destination we took three attempts to find the place where we could check-in for the boat cruise tomorrow.

The hotel room we got is extremely nice, with a bathtub of monstrous proportions, two bathrooms, a kitchen and a spacious balcony.

\paragraph{31. October, about Noon; Aboard the Iceberg}
We have set out to sea.
Weather is great.
I do not know the nautical term but I would say sunny with a little wind.
Sea is calm.
Not that it matters much, we are only doing some freshwater pirating anyways.
We have got two men looking to us not getting lost on or off the boat.
Skipper seems to have done this his whole life.
Only reason he takes passengers at the moment seems to be that he ran out of money.
Hard to understand by Swiss standards.
Easygoing folk in this country.

Apparently the ship needs about five people to set sail but only about 2 to operate it once properly prepared.
Michael and me got the honors of pulling up the sail.
Luckily there was barely any wind.
We have had a hard time as it was.
Besides the five of us and the crew, we have got another 6 people on board.
There is what appears to be two couples and two women. Scotsgirls, Germans and some other nationalities.
Might look into that later.

It is a pretty quiet mode of transportation unless you need to start the diesel engine.
But with the current weather, enjoying the quiet on deck will lead to sunburn pretty quickly.

Thus I am writing this below deck.
Partly because there is nothing table-like above, and partly because I would manage to toss both log book and pen overboard somehow.

Some things, however, still loom above the cruise.
The toilet is electric and ca not handle much besides human end product and a little toilet paper.
An the shower is integrated into the toilet and you have to pump the box dry afterwards.

Also a lesson for shipbuilders.
Stoves on a ship need to be hanging freely.
Otherwise everything will just tip over in rough sea.

\begin{center}
\begin{tabular}{||c||}
\emph{Achievement unlocked}\\
"Sailing 101"\\
\multicolumn{1}{||p{0.8\textwidth}||}{\footnotesize - Get life jacket instructions} \\
\multicolumn{1}{||p{0.8\textwidth}||}{\footnotesize - Know the difference between sailing side and suiside} \\
\multicolumn{1}{||p{0.8\textwidth}||}{\footnotesize - Raise the main sail} \\
\multicolumn{1}{||p{0.8\textwidth}||}{\footnotesize - Yarr!} \\
\end{tabular}
\end{center}

\paragraph{31. October, Afternoon; Aboard the Iceberg}
We have had a casualty.
Well, actually two casualties.
The Preceptress stubbed her toe when boarding the boat.boat.
Looks like some sort of family curse.
Red October seems to have trouble getting on small boats as well.
Second casualty is perception of time.
I am pretty sure it is afternoon, but my main indicator is Rod (the first-and-only-mate) preparing dinner.

We have done some snorkeling in a fish laden bay - Blue Pearl Bay.
With all the coral, shimmering fish and strange little red floaty stuff.
We have agreed the floaty stuff is \emph{not} fish poo.
We also suspect we are the only ones who have brought booze on board.
Everyone else is just too darn responsible.
I suspect we will have to pay a round tonight.

Secondly, we were marooned on a deserted sand bank for an hour of forced relaxing.
Sunburn imminent.

\begin{center}
\begin{tabular}{||c||}
\emph{Achievement unlocked}\\
"But Why Is The Rum Gone?"\\
\multicolumn{1}{||p{0.8\textwidth}||}{\footnotesize - Get marooned on a deserted island} \\
\end{tabular}
\end{center}

\paragraph{1. November, Noon; Aboard the Iceberg}
Had a good night's sleep aboard.
We were anchoring in a quiet bay somewhere north of the whole Whitsunday area.
I kept waking up to the sound of water splashing up against the hull.
Bunk was lacking height too.
I kept bumping into the ceiling.

The night sky the eve before was beautiful.
It was not dark enough to see the milky way but there were hell of a lot of stars.
Actually \emph{everyone} brought booze, so no issues there.

Breakfast was good, then we went for another snorkeling tour.
More reef this time, more diverse fish too.

The Gadgeteer got seasick, woke up with a headache and discarded breakfast.
Got him to recuperate on the beach during the land trip.
He is not sick any more.
Still has some of a headache.

Saw a snake, a few manta rays and beach sharks and some turtles.
For some reason The Preceptress goes nuts for turtles.
Now it is time for lunch and some light sailing.
Home harbor awaits.

\begin{center}
\begin{tabular}{||c||}
\emph{Achievement unlocked}\\
"Turtles All The Way Down"\\
\multicolumn{1}{||p{0.8\textwidth}||}{\footnotesize - See turtles} \\
\end{tabular}
\end{center}

\paragraph{1. November, 17:55; Peppers, Room 114}
We are back at base camp.
There was some 30° sailing, The Gadgeteer got better but us now sunburnt.
Red October secured a Scottish phone number and a French meeting tonight at 8.
Other than that everyone was glad to get back and showered.
The Preceptress tested the hotel pool.
And we had to phone the reception to get our fifth bed and the luggage we deposited during the ship trip.

\begin{center}
\begin{tabular}{||c||}
\emph{Achievement unlocked}\\
"Gone With The Wind"\\
\multicolumn{1}{||p{0.8\textwidth}||}{\footnotesize - Go on a sailing cruise} \\
\end{tabular}
\end{center}

\paragraph{2. November, 14:00; Road to Rockhampton}
We are on the road.
Again.
Going another 500km south.
Not much difference in the landscape from the previous drive.
Grasslands, trees and sugar cane everywhere.

Yesterday evening we concluded the day by going drinking with the French traveleress we met on the boat.
General fun was had even though the live music was loud and we ran into the language barrier a few times.
We were not going very fast, so no harm done.

Well, back to watching the landscape zip by.

\paragraph{2. November, 15:20; Road to Rockhampton}
We just passed road side sign trivia.
The largest mountain in Queensland seems to be Mount Bartle Frere.
There is disappointingly little content.
There was but a single trivia question.
Nobody knew the question anyway.

\paragraph{2. November, 18:00; Villa Mar Colina, \emph{Penthouse}}
We got to Yeppoon.
We checked in.
We got an upgrade\dots{} \emph{Penthouse}, baby!
Downside: We only have three queen size beds.
Downside: The spa is out of order.
Upside: We got the bloody \emph{Penthouse}.
The Gadgeteer just ran around photo-documenting the whole salon\footnote{about as big as my whole flat}, the veranda\footnote{about as big as my whole flat}, the upper deck terrace\footnote{about as big as my whole flat} and the bathrooms next to the main bedroom\footnote{about as big as my whole flat}.
There is a giant TV, a sofa that seats 8+, a kitchen\footnote{about as big as my whole flat}. Okay maybe I \emph{am} exaggerating a little\ldots{} but we got the bloody \emph{Penthouse}!
Tonight will be take-away Thai and Jack Daniels.
Just a bloody drop of extra luck and we would be slurping Margaritas in the jacuzzi.
We even got an ice machine with crusher.

\begin{center}
\begin{tabular}{||c||}
\emph{Achievement unlocked}\\
"Rockstardom!"\\
\multicolumn{1}{||p{0.8\textwidth}||}{\footnotesize - Rent the Penthouse} \\
\end{tabular}
\end{center}

\paragraph{2. November, 12:05; Villa Mar Colina, \emph{Penthouse}}
Fetched Thai food\footnote{take-away} for dinner.
Once again we disregard the 15AU\$ rule and ordered way too much.
Anyways, we filled up and ate way too hot as well.
We got the food up the 45 degrees sloped road the current hotel is built on and the spicy food soaked my shirt.
First action after dinner: shower.

And once again we run into timing issues because Aussies only work until 4pm or so resulting in very hard-to-meet deadlines for check-ins or car-pickups in the afternoon.
Particularly when you are traveling during the whole day.

At least engineering once more provides us with Internet access.

The toilet paper has taken quite a beating so far.
I think the salt water spray is targeting one of the roll's weaknesses.

\paragraph{3. November, 10:30; Road to Hervey Bay}
Elvis has left the Penthouse.
Breakfast, packing, checkout.
As always, we are back on the road.

Also, we have just entered a road with a sign: "Slow trucks - carrying explosives - next 2km".
Then we passed road works and while we waited a truck drove by carrying a dozen bags full of ammonium nitrate\ldots{}
Followed by a truck carrying cement.
Our guess is if the former actually explodes, the latter can just fill on the crater reducing the impact on the following traffic to a minimum.
Hmm, I wonder why there is a road works right at this location.

\begin{center}
\begin{tabular}{||c||}
\emph{Achievement unlocked}\\
"Elvis Has Left The Building"\\
\multicolumn{1}{||p{0.8\textwidth}||}{\footnotesize - Check out of the Penthouse} \\
\end{tabular}
\end{center}

\begin{center}
\begin{tabular}{||c||}
\emph{Achievement unlocked}\\
"How's My Explosion? Call 257-GOESBOOM"\\
\multicolumn{1}{||p{0.8\textwidth}||}{\footnotesize - Drive behind a truck carrying combustibles} \\
\multicolumn{1}{||p{0.8\textwidth}||}{\footnotesize - Drive past a truck carrying explosives} \\
\end{tabular}
\end{center}

\paragraph{3. November, 22:15; Fraser Lodge Holiday Park}
I have done some more driving today.
Aussies drive on the left, so it is advisable to follow their example.
I have never driven an automatic shift before, so Red October is explaining to me when to engage the park gear.
After in depth analysis, I conclude he just wants to convert me to his driving religion.

Bit if an embarrassment are the armatures, since they are mirrored.
Hence I sometimes wipe the front shield instead of signaling.
This identifies me as 100\% genuine tourist, which luckily, I am.

\begin{center}
\begin{tabular}{||c||}
\emph{Achievement unlocked}\\
"Multiclassing"\\
\multicolumn{1}{||p{0.8\textwidth}||}{\footnotesize - Have the log book writer drive at least 500km} \\
\end{tabular}
\end{center}

\paragraph{4. November, 8:50; Barge to Frazer Island}
Ahoy captain, thar land lubber's metal carriage be safely secure on der barge.
Tharr, bring the scurvy ridden bastard that screwed up the ticket computing system.
I shall have 'im hauling keel in a widdles moment.
'Tis no way for a pirate to set over seas with a handwritten ticket.
Arr, shiver me timbers, that lad will feel me wrath.

At least there be sandwiches for the lot of the crew.
And soon the rusted hinges of da metal monstrosity we loaded shall taste the salty sands of Frazer Island.
No dingo, not even one currently in whelping season, shall stop those mighty tires.
Set sail mates and do not forget them 4 wheel drive thingy.
X marks the spot, mind ye.
Stinking landlubbers won't know whot hit 'em.

\begin{center}
\begin{tabular}{||c||}
\emph{Achievement unlocked}\\
"Is Your Light On?"\\
\multicolumn{1}{||p{0.8\textwidth}||}{\footnotesize - Have the foot on the brake on a barge} \\
\multicolumn{1}{||p{0.8\textwidth}||}{\footnotesize - Have someone remind you your lights may still be on} \\
\end{tabular}
\end{center}

\paragraph{4. November, 10:05; Eurong Beach Resort}
Did a first few kilometers of 4WD driving.
Already had to dodge other incoming cars.
Also had first encounters with loose sand.
Obviously operating the gear box is a bit tricky, and the feeling on how much you need to force your car to the it out of sand is still not very well established.
Next part is beach-driving, which means sea-evading.

\paragraph{4. November, 16:15; King Fisher Bay Jetty}
Rewinding the day up to the point where we got on the \ldots{}

\ldots{}we passed a grate, we guess it is for holding off wildlife or to scrape sand off vehicles.
Whatever it was for, it was the innuendo to a day of bumpy, slidy, sandy driving.
Then we were stuck between the surf and the bush. an a pretty wide, pretty unmarked and pretty unpredictable road.
You can choose to drive on dry sand dunes.
Where you get stuck.
Or you can drive near the water's edge, where you can be washed over by waves, destroy your car and yes, get stuck.
Technically you are supposed to drive on the wet strip of sand just between the tide kissed strip and the dunes.
However - this is where \emph{everyone} wants to drive - including incoming traffic and planes.
Yes, \emph{planes}
They land on the beach - occasionally.

\begin{center}
\begin{tabular}{||c||}
\emph{Achievement unlocked}\\
"No Air Control?!?"\\
\multicolumn{1}{||p{0.8\textwidth}||}{\footnotesize - Give way to a landing plane} \\
\end{tabular}
\end{center}

And there are rain water creeks, slowly but persistently washing out neat dips in the sandy driveway.
And there are rocks, blocking the path where you would want to be driving.
And stopping on sand is very drifty business.
So it is fun for the whole family, unless you want to bring your car back undented, unsaltwatered, unsteeringaxledistorted and unheadbumped.
Still there was some driving through semi-deep creeks with lots of splashing water.

Sand highway issues aside, we arrived at our first destination, the landmark ship wreckage of the "Maheno". It is one big heap of rusted metal just sitting on the beach, decaying, yielding to the spray and the time, slowly.
We managed to not dig the car in, as we did the first time we stopped at Eli Creek.
Though, cutting the drivers some slack, driving on sand is somewhat different from any driving you get back home.
And we got out of anywhere, even without having to release tire pressure or other voodoo.

\begin{center}
\begin{tabular}{||c||}
\emph{Achievement unlocked}\\
"Holiday Highway"\\
\multicolumn{1}{||p{0.8\textwidth}||}{\footnotesize - Drive a car on the beach} \\
\end{tabular}
\end{center}

Racing the tide back to Eurong Beach Resort we actually used one of the rock bypass routes.
Though I just scouted ahead and was not in the car during the passing.
It looked slightly bumpy.

We beat the clock and tore through the sandwiches The Preceptress prepared like scavenging dingoes.
Of which we saw none during the trip by the way.

After a quick driver switch we headed inland o one of the lakes.
Roads were pretty to uglyly bumpy but be got through anyways.
Lake looked nice, had quite some visitors and we stayed only shortly.

\bigskip

\begin{tabular}{p{0.85\textwidth}}
\hline
\footnotesize The driver switch actually took place during the stay at the wreck.\ldots{}\\ 
\multicolumn{1}{r}{\footnotesize \textbf{The Chronicler}} \\
\hline
\end{tabular}

\bigskip

\texttt{>>> FILE ACCESS ERROR - MISSING IMAGE <<<}

One drive down to Central Station, one stroll along the jungely creek and one driver switch later we were on the last stretch down o Kingfisher Bay, where we would catch out barge back to the mainlands.

First part was bumpy and foresty.
The second part was a sandy slippery slope from hell.
Most was downhill on extremely fine and extremely dry sand.
It felt more like riding a bobsled than an actual 4WD car.
I thing we used up some fortune cookies on that drive.

Remarkably, the scenery changed abruptly during the drive, from a spring jungle to an autumn forest at the blink of an eye.
Possibly the result of a fire as it changes to completely barren burnt trees just as quickly as it goes back to lush green.
Had to dodge two tourist buses too during that ride.
Scary stuff.

And the latestest part was a criminally steep, criminally bad kept stretch of roller coaster.
No, I refuse to call that \emph{road}.

To top everything up, when we finally got back on sealed road.
We did not manage to get back into 2WD drive mode.
Luckily Aussie Trax, our renter, had an office right around the corner.

So we are on the barge now.
In 2WD.
Tired.
Heading for dinner and getting rid of the rolling heap of rust and sand we spent the day in.

\begin{center}
\begin{tabular}{||c||}
\emph{Achievement unlocked}\\
"Off Road!"\\
\multicolumn{1}{||p{0.8\textwidth}||}{\footnotesize - Drive a 4WD car where you \emph{really} need to drive a 4WD} \\
\end{tabular}
\end{center}

\begin{center}
\begin{tabular}{||c||}
\emph{Achievement unlocked}\\
"X Marks The Spot"\\
\multicolumn{1}{||p{0.8\textwidth}||}{\footnotesize - Visit the site of a stranded shipwreck} \\
\end{tabular}
\end{center}

\begin{center}
\begin{tabular}{||c||}
\emph{Achievement unlocked}\\
"Now \emph{Dig}!"\\
\multicolumn{1}{||p{0.8\textwidth}||}{\footnotesize - Get a car stuck in sand} \\
\multicolumn{1}{||p{0.8\textwidth}||}{\footnotesize - Get a car unstuck in sand} \\
\end{tabular}
\end{center}

\begin{center}
\begin{tabular}{||c||}
\emph{Achievement unlocked}\\
"Landing Maneuver"\\
\multicolumn{1}{||p{0.8\textwidth}||}{\footnotesize - Park your car on a barge} \\
\multicolumn{1}{||p{0.8\textwidth}||}{\footnotesize - Drive your car off a barge} \\
\end{tabular}
\end{center}

\paragraph{4. November, 22:10; Fraser Lodge Holiday Park}
Had dinner at Hog's Breath Cafe: "Best Steak in Australia". Most tender steak I ever had.
The Preceptress is drunk on a single glass of wine.
The rest is hugging the Internets.
Tomorrow will be a lazy day out.
Breakfast at 9 o'clock!
Next they will be handing out napkin holders and massage cushions for the car.

\paragraph{5. November, 10:30; Road to Brisbane}
On the road again.
\emph{singing}
On and for the record, yesterday's drivers were The Gadgeteer an The Bomber.

\begin{center}
\begin{tabular}{||c||}
\emph{Achievement unlocked}\\
"POW!"\\
\multicolumn{1}{||p{0.8\textwidth}||}{\footnotesize - Pass the debris of a tire} \\
\multicolumn{1}{||p{0.8\textwidth}||}{\footnotesize - Pass the truck that lost that tire} \\
\end{tabular}
\end{center}

\paragraph{5. November, 21:05; Brisbane Gateway Resort}
Visited Lone Pine Koala Sanctuary.
The odor was overwhelming.
The cashier could not tell me what exactly was responsible for it, be it the koalas themselves or just the males with their monstrous scent glands or just the rotting eucalyptus leaves they are feeding them.
Whatever it was, the cashier was working there for so long, she did not even smell it any more.

Also, the "wildlife park" as it calls itself did not even hand out tickets to customers.
So I had to staple the food shop receipt into the log book.
Sad stuff.

"Wild" is also a bit of an exaggeration, the most active animals were the platypus and the four dingoes.
The rest was lying or sitting around, dozing or generally looking stoned off their asses.
Winners of the lethargy award were the koalas, hands down.
They spend an average of 19h a day sleeping in on a tree branch.
The kangaroos, emus and wombats came in close second.
Especially the 'roos excelled at looking somewhat high on weed.
Maybe it is all the eucalyptus farting koalas that gets to them.

Personal favorite of mine were the Tasmanian devils.
cute little angry balls of omnivorous fluffiness.
Certainly better than the big furry buttocks in the sky.

Most of the park was occupied by lizards and bush turkeys in a never ending struggle for who gives the least fucks about the visitors.

Highlight of the day was driving to one end of Brisbane only to realize that there is more than one School Street in Brisbane, and our apartment for the night actually is on the \emph{other} end of the town.

\begin{center}
\begin{tabular}{||c||}
\emph{Achievement unlocked}\\
"User Error"\\
\multicolumn{1}{||p{0.8\textwidth}||}{\footnotesize - Punch the wrong address into your navigation system} \\
\multicolumn{1}{||p{0.8\textwidth}||}{\footnotesize - Realize this when you physically get to that location} \\
\end{tabular}
\end{center}

\paragraph{6. November, 7:40; Brisbane Gateway Resort}
Sunday, bloody Sunday.
Woke up at seven, strolled around the park.
Was bored beyond belief.
Everything opens at 8am, pool, reception, guest room, tennis court\ldots{}
Gonna be a slow day.

\paragraph{6. November, 22:40; Brisbane Gateway Resort}
Mountain top first, then we hit a botanic garden. Seen cacti, bonsai trees and fern. So there was mostly photos taken and not much to write.

Dinner was, as suggested by The Bomber, at Breakfast Creek Hotel.
Great steak, great dessert, too much cider on my account.

Navigating Brisbane is problematic, not as problematic as Melbourne but still windy, complicated and riddled with road works.
