\chapter{Week One}

% 17th October til 23th October

\paragraph{17. October, 11:15; On the road to Wagga Wagga}
After Sydney was done confusing the heck out of our navigation system, we are now trucking the countryside after leaving the suburbs.

Roadkill counters are steadily increasing.
Had 4 kangaroos and a wombat so far.

\begin{center}
\begin{tabular}{||c||}
\emph{Achievement unlocked}\\
"Wild Unlife"\\
\multicolumn{1}{||p{0.8\textwidth}||}{\footnotesize - Have the first native animal you see be roadkill} \\
\end{tabular}
\end{center}

\paragraph{17. October, 11:30; Road through Jenolan Forest}
We are more or less the only car on the immediate road.

We are passing rolling hills, eucalyptus trees, pine trees, eucalyptus trees and pine trees.

\paragraph{17. October, 13:20; Jenolan Caves}
Gone spelunking, or near-spelunking.
There was a large cave, a dam with emerald waters - or maybe turquoise waters, who can tell these days.
There were eucalyptus trees in a large clearing further down the valley.
The Gadgeteer scared a dragon, then photographed it.
The rest just scared regular lizards.

Pecularity: Part of the walkway through the cave doubled as road.
A sign advised us to use extreme care when passing.
Had only regular care at our disposal, survived nonetheless.

When we got back to the car, one of the guided tours was just starting.
They were calling for "chicken holders" - comedy ensued.

\texttt{>>> FILE ACCESS ERROR - MISSING IMAGE <<<}

\paragraph{17. October, 14:30; Oberon}
Picked up a sammitch, a pastie, two pies, two hamburgers and a chicken salad.

The pies will most likely end up in trash, leaving The Preceptress hungry and the chicken salad was a bit improvised.
Rest was good though.

Fascinatingly, parking forwards is prohibited.

\paragraph{17. October, 21:40; Motor Inn Wagga Wagga}
We arrived at sunset.
Tires digging through the gravel in the driveway.
Doors looked barred.
A few cars rust silently in the parking lot.
Our headlights fall dark.
Car doors slam shut.
Nobody notices our arrival but the cold evening breeze.
The outer door creaks as we enter.
The inner door slams shut.
A dark saloon looms beyond.
Chairs stored on the tables.
It was swept, dust had not yet settled in.
We walked past a flickering TV screen, sume kids rustled around.
Beyond, the reception desk.
We checked in.

Dinner at pub.
The Bomber fails to buy Skittles from a dispenser.
Outside LEDs hanging from a tree glitter in the night.

\texttt{>>> DISTANCE TRAVELED BY CAR: 600km - totals 600km <<<}

\paragraph{18. October, 9:40; Highway to Cooma}
This is cow country, the secret cow level, cowtopia, the great grazing grounds,
the place a good cow is reincarnated to when it has been made into enough delicious burgers.
In Switzerland we have a label "Freilandhaltung", when they are kept outside, on the field.
Compared to the rolling grasslands we pass now, where the cattlegrounds go on until they meet the horizon,
the label seems like a bad joke.

If you ever plan on reincarnating as a cow. Try to get a spot in Australia.
You are going to get eaten anyways.
Might as well choose a nice place to stay until that time.

\paragraph{18. October, 11:35; Black Perry Lookout}
We now have even seen \emph{live} cangaroos and emus and have made our way over the Snowy Mountain Road.

A quick stop at the lookout shows a lot of foresty mountainside.

\texttt{>>> FILE ACCESS ERROR - MISSING IMAGE <<<}

And we greeted old people which seem to follow plans analogous to ours.

Since we are going to drive onward now, I continue writing in the back seat while insane bikers pass by.
Should work, bit I notice my handwriting suffers during the bumpy ride.

One stop back we strolled down the side of a lake.
Fairytale weather and a tree which could have sprung from any jolly children's story later we were back on the road.

\texttt{>>> FILE ACCESS ERROR - MISSING IMAGE <<<}
 
\paragraph{18. October, 13:40; Snake Trail}
We hit a snake trail, diverting from the highway to the left.
Gravel road is bumpy.

The pen rolled under the seats somewhere.
I am unable to find it, so I am using a pencil for this entry.

We ditched the plan to take the scenic drive along the mountainside.
Would have taken us the whole day just for the drive and no time for exploring.

So we went spelunking.
Big wet cold cave.
Contained a wig.
Entrance hall collapsed some time ago.
Owner did not come around to renovate.
Must have come on hard times - the lighting was sparse and most of the rooms were damp.
At least they had outdoor heated pool, but be skipped that.
Always prioritize food.
Just noticing.
If I keep this speed of logging up, I might fill the log book before wee are back out.

Maybe I should remember to hit an office supply shop for a spare paper blank.

The toilet paper is still untouched.

\paragraph{18. October, 15:00; Exiting Cabramurra}
At Australia's highest up village thae café closes it's kitchen at 1400.
We settled for Cup Noodles - well - some of us did.
The others maintian their sugar levels with sweets and candy bars.

We skipped photographing the town sign and I found my pen.

\texttt{>>> DISTANCE TRAVELED BY CAR: 275km - totals 875km <<<}

\paragraph{19. October, 9:00; Exiting Cooma}
Had delicious (and plentiful) dinner last night, followed by an attempt at wireless internet.

\begin{center}
\begin{tabular}{||c||}
\emph{Achievement unlocked}\\
"Evolution 101"\\
\multicolumn{1}{||p{0.8\textwidth}||}{\footnotesize - Run over a Cuckaborra} \\
\end{tabular}
\end{center}

\begin{center}
\begin{tabular}{||c||}
\emph{Achievement unlocked}\\
"Backseat Driving"\\
\multicolumn{1}{||p{0.8\textwidth}||}{\footnotesize - Start a Flame War with the driver} \\
\end{tabular}
\end{center}

Wireless internet was slooow.
Too slow for Lotus Notes, preventing The Bomber to check his work mail.
Too slow for GMX, preventing The Preceptress to check her private mail.
Almost too slow for GMail enabling me to do reauthentification at snail's speed.

While I was logging we had our first road kill.
It might have been a good thing.
That Cuckaborra was too stupid for life.
Just waiting in the middle of the road, staring at the set of wheels approaching at high speeds.
Maybe it was suicidal.
Who knows.

\paragraph{19. October, 9:25; On the road}
I think we just passed a road called \emph{No Through Road}.

And we missed the exit to Springfield.

\paragraph{19. October, 12:22; Still on the road}
Driving, driving, driving - on roadkillless raods.
Passing meadows, fences, forests, sheep, cows, cars, horses, birds, traffic signs and concealed entrances.

Trying to point out to the others what I have dubbed \emph{Sheep Launch Pads}: Small ramps that are directed outwards from a corral and lead to virtually nowwhere.
Suppose they are intended to serve as a way to get sheep out to the meadow without giving them any way to come back.

\paragraph{19. October, 15:40; Mallacoota}
Starting to get the hang of Australian serving sizes.
Ordering a single meal or a large side usually is enough.

Took a stroll on the beach.
The Bomber and me were thwarted from crossing to the other shore by Six Meters Of Water.
Noticeable amounts of shell were discovered.
There was beautiful sea, sand and waves.
Work stress debuff starting to wear off.
The Gadgeteer took about 2 Minutes of me talking Irish on the shore.

No, I am not going to transcribe.

\paragraph{19. October, 17:15; Road to Lake's Entrance}
The sun is descending slowly on a sky barren of clouds.
As we pass the flickering shadows of the forest we plow through legions of insects swarming in the dry spring air.

\texttt{>>> FILE ACCESS ERROR - MISSING IMAGE <<<}

\begin{center}
\begin{tabular}{||c||}
\emph{Achievement unlocked}\\
"Buzzkill"\\
\multicolumn{1}{||p{0.8\textwidth}||}{\footnotesize - Squish 100 bugs with your wind shield} \\
\end{tabular}
\end{center}

\begin{center}
\begin{tabular}{||c||}
\emph{Achievement unlocked}\\
"Beyond Inadequate Bovine Rivers"\\
\multicolumn{1}{||p{0.8\textwidth}||}{\footnotesize - Pass Bad Cow Creek} \\
\end{tabular}
\end{center}

\paragraph{19. October, 17:30; Fluffy Forest} 
Passing through a forest which seems to have burnt down.
However from the dead trunks the leaves just sprout once again.
The whole forest looks like green corran candy sticks.

\emph{It's so fluffy!}

\texttt{>>> FILE ACCESS ERROR - MISSING IMAGE <<<}

\begin{center}
\begin{tabular}{||c||}
\emph{Achievement unlocked}\\
"The Best Things In Life\ldots{}"\\
\multicolumn{1}{||p{0.8\textwidth}||}{\footnotesize - Obtain free good quality wireless Internet access} \\
\multicolumn{1}{||p{0.8\textwidth}||}{\footnotesize - You must have already had paid bad quality wireless Internet access before to unlock this achievement} \\
\end{tabular}
\end{center}

\paragraph{19. October, 22:25; Lake's Entrance, Room 5}
First life sunset in Australia.
We saw it from the beach.
Romantic.
We had the whole program.
Rolling waves.
Endless horizon.
The sun going through the orange tones down to red.
Boats glistening in the duskish shine.
Masts rocking in the evening tide.
The frequency of photographs taken peaked.
The remaining digital storage capacity tanked.

We went for Mexican this night.
Had to find out that any dish that costs about 15 Australian Dollars will be a regular sized meal.
Anything which costs more will be challenging to finish.
At least this is the case while away from the big cities.

\texttt{>>> DISTANCE TRAVELED BY CAR: 452km - totals 1325km <<<}

\paragraph{20. October, 9:30; Lake's Entrance, Gas Station}
The Bomber, Red October and me went for a run on the beach at dawn.
Damn I am out of shape.

Once again we refuel.
Must have burnt through a dozen dinosaurs already.
Damn van is a fuel guzzler.
And the fron grill is a war zone.
Or rather - a bug graveyard.
Now we are back on the raod.
Windshields wiped and tires pumped.

Melbourne awaits beyond the horizon.

\paragraph{20. October, 10:10; Road to Melbourne}
After six attempts which ended with the tablet pc crashing and losing the playlist, we finally found an app that does not crash, hang, stop playing when the display turns off or just drops the playlist randomly.
So we now have reliable music in the backgorund without having to rely on Aussie radio, which is - according to everyone in the car - just plain horrible.

\begin{center}
\begin{tabular}{||c||}
\emph{Achievement unlocked}\\
"\ldots{}whut?"\\
\multicolumn{1}{||p{0.8\textwidth}||}{\footnotesize - Misunderstand a road name and log Bad Cow Creek instead of Fat Cow Creek}\\
\end{tabular}
\end{center}

\paragraph{20. October, 10:35; Following the railroad tracks}
Australians must be really good at fencing.
Not the kind with sharp sticks.
The kind which involves putting up obstacles to keep wild or domestic life from crossing.

We are passing mile after mile of fences.
Either this keeps wildlife from wandering onto the road (with mediocre success) or it keeps cattle from walking more than a few miles in a sraight line.

The chines built the Great Wall, the Australians just built the Great Fence.

On another note, The Bomber found a better explanation for the \emph{Sheep Launch Pads}.
They are for loading and unloading lifestock into transporters\ldots{}
duh\ldots{}

\paragraph{20. October, 10:50; Sale}
Yes, we just passed Sale, the town.
Since the name was just too silly, we moved along.

\paragraph{20. October, 12:00; Road to Melbourne}
Somehow we ended up in Weird-Names-Country: Baw Baw Mountain, Drouin, Darnum, Robin Hood, Service Centre Bay - now wait, that is no town - Dadenoug, Labertouche.
Got\ldots{} to\ldots{} stop\ldots{} reading\ldots{} roadsigns.

\begin{center}
\begin{tabular}{||c||}
\emph{Achievement unlocked}\\
"Kevinism Country"\\
\multicolumn{1}{||p{0.8\textwidth}||}{\footnotesize - Pass "Sale"}\\
\multicolumn{1}{||p{0.8\textwidth}||}{\footnotesize - Pass "Fat Cow Creek"}\\
\multicolumn{1}{||p{0.8\textwidth}||}{\footnotesize - Pass "Robin Hood"}\\
\multicolumn{1}{||p{0.8\textwidth}||}{\footnotesize - Pass "Baw Baw Mountain"}\\
\multicolumn{1}{||p{0.8\textwidth}||}{\footnotesize - Pass "Wagga Wagga"}\\
\end{tabular}
\end{center}

\begin{center}
\begin{tabular}{||c||}
\emph{Achievement unlocked}\\
"40 Ton Tweezers"\\
\multicolumn{1}{||p{0.8\textwidth}||}{\footnotesize - witness two trucks overtake a third simultaneously on the left and right}\\
\end{tabular}
\end{center}

\paragraph{20. October, 13:00; Approaching Melbourne}
Traffic gets heavier as we cloase on target.
Wind keeps the driver on his toes, as does the lunatic driving style of the Aussie truckers.

We have been passing noise-sheltered suburbs for quite some time now.

\emph{Fucking big town, this Melbourne.}

\paragraph{20. October, 13:30; Hotel Alto Parking Lot}
Parking lot clocks in Melbourne run with pressure sensors.
At least that is what they are telling us.
We had no way of just waiting until The Preceptress and The Gadgeteer had checked in.
The authorities were right on our track, and after our moneys.

\texttt{>>> DISTANCE TRAVELED BY CAR: 317km - totals 1650km <<<}

\paragraph{20. October, 21:45; Melbourne, Room 404}

\begin{center}
\begin{tabular}{||c||}
\emph{Achievement unlocked}\\
"File Not Found"\\
\multicolumn{1}{||p{0.8\textwidth}||}{\footnotesize - Check in to room 404}\\
\end{tabular}
\end{center}

Arrived in hook-turn-notorious Melbourne city.
Hook turns are when you try to take a right turn from the lane on the extreme left.
And it looks like certain suicide when performed.

We split up for the city exploration sice The Preceptress had to organize her flight to New Zealand.
The rest went for a stroll and a coffee in Federation Square.
Though the buildings there were anything but square.
Supposedly the architect drove a few construction engineers to madness.

The city itslf reminds me of San Francisco or even Zurich, except this one feels more like a police state than both of the others.
In the evening we even saw a police car with a supposed sobering cell attached.
Scary prospects for drunkards.

went to a pub \emph{The Local Taphouse} to meet The Preceptress's aquaintances.
Had a nice evening with pub food in a pub that has a different selection of local beers every day.
The group tried a grand total of six beers and one cider.
The general 15 Dollar rule for meals held up, though in the city you have to up it by 3 Dollars.

The district the pub was in laeft an\ldots{} interesting impression. It looked a bit shabby, the buildings were mostly in a desolate state from the outside, yet nice from the inside.
The people seemed friendly if a bit loud for my tastes.

Bumped into a waiter at the end of the evening.
Even though I made him spill a drink, he kept being (overly) friendly.
Though he checked out my table afterwards, I guess he was checking if I might have had one or two drinks too many.

\paragraph{21. October, 14:15; Melbourne, Free Shuttle Bus}
The weather took a turn for the worse.
The Preceptress took up the opportunity to do some laundry, the rest decided to throw themselves at the rain.
Well, not really rain, it was more like overly enthusiastic fog.
We headed out for Chinatown, which was somewhat diasappionting, then went onward to Saint Patricks Cathedral.
Being archbishop of Melbourne seemd to be a dangerous job. Of the seven they have had so far, five already died and one seems to have quit the job before it could take the better of him.
Special thing about the cathedral: Wooden roof.

Now we sit reunited in the free tourist shuttle bud, which runs every 30 minutes, which translates to Australian as "every 25 minutes" which makes catching it quite of a waiting and gambling game.
We missed one because we decided to have a look at graffity lane.
There one of the fundamental truths about mankind was displayed.
Even when graffity is legal, artfully created pictures will still be skribbled over by idiots only capable of reliably misspelling their names.

Fun thing about technology and free bus rides: People will bring cameras and just film the road during the trip.
Maybe one should point out the existence of Google Street View.

\paragraph{21. October, 15:45; Melbourne, Free Tourist Shuttle Stop 1}
Almost completed the circuit, since we did not get in at the official starting point to be gin with, we will stay on a few more stops.

Forgot to mention that we hit Melbourne Museum, got bummed out on the same old colonialism issues you have everywhere.
Saw some Melbournian history and a horse that seemed very Australian and very famous.
Though it died somehow in the USA.
Gotta look that up.
I guess it ended up covered in gravy and accompanied by chips courtesy of some angry mob bookies.

\paragraph{21. October, 23:05; Hotel Alto Room 404}
The horse died of an overdose of arsenic according to Wikipedia.
No evidence of a crime was ever found.

On another note we had (expensive) Japanese food for dinner.
The Australian serving sizes failed us this time.
Seems that Japanese food always comes in normal size servings, regardless of price.
Had Wagyu beef for dinner - delicious but pricey.

The we - minus The Preceptress - headed to the top of Eureka Tower.
The viewing facility was named Skydeck 88 and was reasonably high up.
Still too high up for me to feel comfortable on the terrace when the wind blew.
The view was nice though.
Lots of lighting and little cars moving in the streets and ways of slipping and crshing through a window and plummeting to \ldots{}
As I said before, waaay to high up to feel comfortable.

\begin{center}
\begin{tabular}{||c||}
\emph{Achievement unlocked}\\
"Point of No Return"\\
\multicolumn{1}{||p{0.8\textwidth}||}{\footnotesize - Witness someone propose a few hundred feet above solid ground}\\
\end{tabular}
\end{center}

\begin{center}
\begin{tabular}{||c||}
\emph{Achievement unlocked}\\
"Liberate Wall Street!"\\
\multicolumn{1}{||p{0.8\textwidth}||}{\footnotesize - Witness Wall Street protestors protesting}\\
\multicolumn{1}{||p{0.8\textwidth}||}{\footnotesize - Witness Wall Street protestors being cleared away by the police}\\
\end{tabular}
\end{center}

\paragraph{22. October, 8:25; Hotel Alto Room 404}
Getting ready to hit the road.
Electric shavers buzz over unsuspecting facial hair.
Bickering an moaning colours the conversations.
The shower runs wet with water and towels are drenched mercilessly.

Now all that remains is to stuff my coffer and hit the road.
Though we really should have breakfast first.

\paragraph{22. October, 10:40; Road to Apollo Bay}
We have cleared the crowded, convoluted and confusing streets of Melbourne.
Even the GPS navigation system was going insane inside the web of hook turns, traffic lights and road works.

Back on the highway the road is clear, but heavy rain is settling in.
We planned for some sightseeing on today's strech of road.
Maybe we will skip that.
Unless we want to prove our water-proofness.

\begin{center}
\begin{tabular}{||c||}
\emph{Achievement unlocked}\\
"Wide Load"\\
\multicolumn{1}{||p{0.8\textwidth}||}{\footnotesize - Bump your read mirror into a parked truck without breaking it}\\
\end{tabular}
\end{center}

\paragraph{22. October, 12:15; Road to Apollo Bay}
Took a stroll along Danger Point.
At lease it stopped raining but the weather is still ghastly.
The surfers seem unimpressed, straddling the waves despite the cold.
Dafying the rocky ground and the chilling winds.
\emph{We} get back in the car.

\paragraph{22. October, 12:45; Anglesea Golf Club}
Stopped at a golf club which is notorious for having kangaroos on its premises.
It \emph{does} have them.
Also it has big signs telling visitors that they are not permitted to enter the golf course to view kangaroos.
We did anyways, saw a kangaroo, and avoided getting our asses kicked by the local security as well as getting our asses kicked by the local kangaroos.

\begin{center}
\begin{tabular}{||c||}
\emph{Achievement unlocked}\\
"Kangaroo Cup"\\
\multicolumn{1}{||p{0.8\textwidth}||}{\footnotesize - See kangaroos on a golf course}\\
\end{tabular}
\end{center}

\paragraph{22. October, 13:05; Some overrun outlook}
The indians have caught up with us.
I think they followed us from Japan.
We left trying to maximize speed and minimize suspicion.
They were even talking english to cover up their identity.
Maybe I need to start using more cryptic code names.

\paragraph{22. October, 14:35; Lorne Visitor Centre}
Lunch today was a picnic, literally.
We were under siege by seagulls during the whole meal and then cacdoos joined in.
We got out while we could, being spred by bird poo and beak attacks.
Now headed for waterfalls.

\paragraph{22. October, 15:30; Erskin Falls}
It is a waterfall.
Enough said.

\begin{center}
\begin{tabular}{||c||}
\emph{Achievement unlocked}\\
"Leaky Faucet"\\
\multicolumn{1}{||p{0.8\textwidth}||}{\footnotesize - It is a waterfall. Seriously.}\\
\end{tabular}
\end{center}

\paragraph{22. October, 16:55; Grey River Road}
We see grey furry butts in the sky.
That is to say - koalas.
Statistically speaking, more than 50\% of koalas encountered in the wild are sleeping.
So there is not much of a difference between a fur covered branch and a koala.
Not 100\% sure why everyone considers them so cute.

\begin{center}
\begin{tabular}{||c||}
\emph{Achievement unlocked}\\
"Aussie Full House"\\
\multicolumn{1}{||p{0.8\textwidth}||}{\footnotesize - See three kangaroos}\\
\multicolumn{1}{||p{0.8\textwidth}||}{\footnotesize - See two koalas}\\
\end{tabular}
\end{center}

\paragraph{22. October, 19:25; Road back from the lighthouse}
Lighthouse access was closed , walkway through bush was deserted.

Also koalas, koalas! Koalas!! Koalas!!! \emph{Koalas}!!!!

Sorry, had to get that out of my system.

\paragraph{23. October, 9:25; Road to Beech something}
Diverting away from the Great Ocean Road, we head for waterfalls and other pretty sights.
The only road kill seen today is small birds.

\begin{center}
\begin{tabular}{||c||}
\emph{Achievement unlocked}\\
"Secret Cow level"\\
\multicolumn{1}{||p{0.8\textwidth}||}{\footnotesize - Drive by many cows}\\
\end{tabular}
\end{center}

\paragraph{23. October, 10:35; Triplet Falls}
Well, that was another three waterfalls.
Which means water.
Falling.
In the forest.
\emph{Sparkly}.

Along the walk we came across the remains of a sawmill.
Well - what the tourist left of the remains of a sawmill.
The old pioneers brought a multi-man sized steam boiler out into the nowhere to power their saws.
Those were the days.

\begin{center}
\begin{tabular}{||c||}
\emph{Achievement unlocked}\\
"Trail of Terror"\\
\multicolumn{1}{||p{0.8\textwidth}||}{\footnotesize - See one of the terrifyingly menacing carnivorous woodland snails}\\
\end{tabular}
\end{center}

\begin{center}
\begin{tabular}{||c||}
\emph{Achievement unlocked}\\
"\ldots{}but we haven't got the time!"\\
\multicolumn{1}{||p{0.8\textwidth}||}{\footnotesize - Pass "Wait-A-While Road"}\\
\end{tabular}
\end{center}

\paragraph{23. October, 12:35; Twelve Apostles}
Great cliffs thrust into the ocean, waves crash against the rocky shores.
Seaguls screech overhead, circling the lone rock pillars guarding their lonely post in the spray.
We watch and feel the soft ocean breeze whifting across the shrubbery.
Below, the sea is sifting sanf from the shore, patiently scrubbing land from the country, claiming one coastal spire after the other in an endless dance of erosion.

While we keep our feet firmly on the ground The Preceptress goes for a copter ride.
Supposedly it was quite scenic.

\paragraph{23. October, 15:15; Road to Mount Gambier}
We hit the first stretch of straight road.
Red October tells us there will be much longer and much straighter roads in the Red Center.
Not really looking forward to that.

\begin{center}
\begin{tabular}{||c||}
\emph{Achievement unlocked}\\
"133!"\\
\multicolumn{1}{||p{0.8\textwidth}||}{\footnotesize - Drive 200 kilometers in 1.5 hours}\\
\multicolumn{1}{||p{0.8\textwidth}||}{\footnotesize - Use Australia's time zones to cheat during the speed calculation}\\
\end{tabular}
\end{center}

\paragraph{23. October, 21:20; Blue Lake Holiday Park, Apartment B52}

\begin{center}
\begin{tabular}{||c||}
\emph{Achievement unlocked}\\
"Flying Porcupine"\\
\multicolumn{1}{||p{0.8\textwidth}||}{\footnotesize - Stay a night in apartment B52}\\
\end{tabular}
\end{center}

The park is beyond the town, past a volcanic crater filled with what is supposed to be \emph{extremely} blue water.
Only it is \emph{not very} blue this time of year.
I smell marketing fabrications.
This place is also known for dolines, hooray for staying on ground that may give way at any time.

We ate in for dinner, take-away pizza was the keyword.
There was also a teensy problem while driving to and fro the pizza joint.
We disregarded the sign saying only one car at a time should pass the boom.
This exiting the park without punching in our designated pin code.
This in turn led to the system to disallow any car with our key entering the oark.
So our car ended up \emph{outside} the park with the system still believeing it to be \emph{inside} the park.
Hence the system would not allow us to enter.
Being a slightly sophisticated system it was also not possible to trick it into opening the boom when there is no car waiting to leave.
So it essentially prevented us from fixing its belief that our car was still inside without another car that was already inside the park triggering the car sensors.

Our conundrum was solves by a couple of park patrons generously helping out by using their car to fake our car leaving the park.
Jolly good fun was had by all parties involved.
Except maybe the boom.

\begin{center}
\begin{tabular}{||c||}
\emph{Achievement unlocked}\\
"Wayne Industries"\\
\multicolumn{1}{||p{0.8\textwidth}||}{\footnotesize - Find out that Melbourne was founded by Batman}\\
\end{tabular}
\end{center}

\begin{center}
\begin{tabular}{||c||}
\emph{Achievement unlocked}\\
"Cooperative Testing Initiative"\\
\multicolumn{1}{||p{0.8\textwidth}||}{\footnotesize - Use two cars to unlock the park boom, you monster}\\
\end{tabular}
\end{center}

